Notes on scheduling the SAA2019 meeting

### 2017-11-04 analysis/paper/saa2018_posters.Rmd
we have too many posters

# In here we have org and after hours posters
org_and_after_hours_posters_individual <- 
  read_excel("../data/raw_data/Organized Session Abstracts_2018_AB.xlsx") %>% 
  filter(`Session Type` == "Poster Symposium")

@@

posters_with_abstract_ids <- 
all_of_the_day_parts %>% 
  filter(!is.na(`Abstract Id`)) %>% 
  group_by(day_part_from_while) %>% 
  tally() %>% 
  summarise(sum(n)) %>% 
  pull()
```

>>>>

# In here we have org and after hours posters

all_abstracts  <-  read_excel("../data/raw_data/Organized Session Abstracts_2018_AB.xlsx")

org_and_after_hours_posters_individual <- 
all_abstracts %>% 
  filter(`Session Type` == "Poster Symposium") %>% 
  filter(Role == "Presenter")

gen_and_org_poster_sessions_only <- 
all_abstracts %>% 
  filter(`Session Type` == "Poster Symposium") %>% 
  filter(Role == "Chair (Primary)")

@@

# why is each poster in each day-part?
all_of_the_day_parts %>% 
 arrange(uid) %>% View

# how many abstracts
posters_with_abstract_ids <- 
all_of_the_day_parts %>% 
  filter(!is.na(`Abstract Id`)) %>% 
  group_by(day_part_from_while) %>% 
  tally() %>% 
  summarise(sum(n)) %>% 
  pull()
```
